University \emph{class scheduling} problem (UCSP) is faced each academic term
by many academic institutions throughout the world. A sufficient number of classes must
be created and then assigned to the students and professors in such a way,
that persons' schedules don't intersect and the persons are (rather) satisfied
with the assignment. It is usually done manually.

While UCSP research has already started by 1960s,
no accessible computational equipment had the resources to handle the problem
in general and/or for entire universities until the recent times.
With rapid computer performance growth in the 1990s, computationally
difficult problems could be researched with minor expenses and many
solution search methods were developed for various kinds of problems.
\medskip

\noindent
This \thisdoc\ proposes an extendable UCSP solution with support for
\emph{schedule personalization}. The latter means that the solutions takes
into account \emph{personal} preferences of the represented people.
The solution is based on \underline{agents negotiations} between the
representatives of \emph{students/groups} and \emph{professors}.
The representing agents permit defining \emph{personal preferences} and
\emph{restrictions}, that are described using the concept of \emph{coherence}
and are used to optimize individual schedules.

% The complete university schedule --- the result of a successful negotiation,
% is the union of all the individual ones.

The problem was considered in a generic manner (for no specific university), that
lead to a number of simplifications and assumptions. The results of applying the
proposed method to test data were found satisfactory. Nevertheless, a number
of possible improvements is presented.
