\documentclass[../header]{subfiles}

\begin{document}

\providecommand{\rootdir}{..}
\input{\rootdir/MathDefs}


\subsubsection{Solving UCSP with Genetic Algorithm}
\label{sec:GA-UCSP}
Genetic algorithm was used to optimize university schedules at Tabriz university
\cite{UCSP-GA}. The scheduling was done for four groups, considering
\underline{some opinions} of the institution and the professors.

The problem at the article is defined by:
\begin{enumerate}
  \item a set of lectures;
  \item a set of subjects;
  \item a set of timeslots, where each timeslot consists of
    \begin{enumerate*}[1)]
      \item day of week (6 days),
      \item item period (4 per day) and
      \item classroom (6 rooms);
    \end{enumerate*}
  \item a set of constraints;
  \item a set of weights (penalties) for the constraints.
\end{enumerate}

The constraints are divided into hard and soft (determined by the corresponding
weight) \cite{UCSP-GA}.
The \emph{hard} ones are \emph{time constraints} for professors, classrooms and
students/groups.
\emph{Soft} constraints include:
\begin{enumerate}
  \item A subject should not be repeated on the same day.
  \item A subject should not be repeated on the consequent day.
  \item No subject should be allocated to a time period that
        heads of department/professors don't demand or find inconvenient.
\end{enumerate}



\bigskip\noindent
A chromosome encodes class instances for the lecturers and is divided in two equal
parts, that represent the first and second class of given subject.
The subjects from the second part correspond to those of the first.
The genes of the first part store the subject and the timeslot assigned, while
those from the second part defined only the timeslot. Genes are ordered by
lecturer and it is known how many classes one gives.

The fitness function used depends heavily on the provided constraint weights:
$\sum\limits_{i=1}^m w_i \delta_i$, where $w_i$ is the constraint weight and
$\begin{cases}
  \delta_i = 0 & \text{if constraint is satisfied}\\
  \delta_i = 1 & \text{if constraint is violated}
\end{cases}$
The task therefore is \underline{minimizing} population fitness.

\end{document}
